---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

```


<!-- badges: start -->

<!-- badges: end -->

This is a package designed to implement color palettes for the SSFRC into `R` and `ggplot2`.  
The package draws some inspiration from the `gameofthrones`-package.  

For questions or suggestions please contact me:

Email: graflukas57@gmail.com 

Twitter: https://twitter.com/graf_gruen 

## Installation

From Github:
```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("graflukas138/sydskog")
```

From CRAN:
```{r, eval=FALSE}
install.packages("sydskog")
```

## Palettes
`sydskog` provides 30 different palettes. An overview can be viewed with the `sydskog_colors()`
function:

```{r}
library(sydskog)

sydskog_colors()
```

# Usage

An example of usage for the `sydskog` - color scales.
The default option is oak.

```{r}
pal <- sydskog(255, option = "oak")
image(volcano, col = pal)
```


## ggplot2
`sydskog` provides color scales and functions to use with `ggplot2`.  
If `ggplot2` is available you'll have access to the `scale_[colour|fill]_sydskog()` functions:

### Continous data

```{r, echo=F}
set.seed(1)
library(ggplot2)
```

```{r, message=FALSE}
ggplot(data.frame(x = rnorm(10000), y = rnorm(10000)), aes(x = x, y = y)) +
  geom_hex() + coord_fixed() +
  scale_fill_sydskog(option="oak") + theme_bw()
```


### Discrete data

Use `scale_fill_sydskog_d()` to plot discrete data.

```{r, message=FALSE}
txsamp <- subset(txhousing, city %in%
  c("Houston", "Fort Worth", "San Antonio", "Dallas", "Austin"))

ggplot(txsamp, aes(x = median, fill = city)) +
  geom_histogram(position = "dodge", binwidth = 15000)+ scale_fill_sydskog_d(option = "oak")+ theme_bw()
```

Order of colors can be reversed using `direction = -1`.

```{r, message=FALSE}
txsamp <- subset(txhousing, city %in%
  c("Houston", "Fort Worth", "San Antonio", "Dallas", "Austin"))

ggplot(txsamp, aes(x = median, fill = city)) +
  geom_histogram(position = "dodge", binwidth = 15000)+ scale_fill_sydskog_d(option = "oak", direction = -1) + theme_bw()
```

